### 2013-05-21 doc/icml2013/intro.tex
Finished lemma 5 and minor changes in supplementary material
Made figure legend black/white, minor language fixes

% Goal of this paper
% This paper: first step in establishing provably correct estimation
% with simple mixture of linear regression
Our broad goal is to develop efficient provably consistent estimators for
discriminative latent-variable models.
In this paper, we provide a first step in this 
direction by proposing a new algorithm for a simple model,
\emph{a mixture of linear regressions} (MLG) \cite{VieleTong2002}.

@@

% Norms
For a matrix $X$,
let $\|X\|_*$ denote the nuclear (trace) norm (sum of singular values),
$\|X\|_F$ denote the Frobenius norm (square root of sum of squares of singular values),
$\|X\|_{\max}$ denote the max norm (elementwise maximum),
$\|X\|_\op$ denote the operator norm (largest singular value), and
$\sigma_k(X)$ be the $k$-th largest singular value of $X$.
For a $p$-th order tensor $X$,
let $\|X\|_* = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_*$ denote
the average nuclear norm over all $p$ unfoldings,
and let $\|X\|_\op = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_\op$
denote the average operator norm over all $p$ unfoldings.

For a tensor $X \in (\Re^d)\tp{p}$, let $\cvec(X) \in
\Re^{N(d,p)}, N(d,p) = \binom{d + p - 1}{p}$ be the collapsed vectorization of
$X$. For example, if $X \in \Re^{d \times d}$, $\cvec(X)
= (X_{ii} : i \in [d]; X_{ij} + X_{ji} : i,j \in [d], i<j)$.
In general, each component of $\cvec(X)$ is indexed by a vector of
counts $(c_1, \dots, c_d)$ with total sum $\sum_i c_i = p$.  The value
of that component is $\sum_{k \in K(c)} X_{k_1 \cdots k_p}$, where $K(c)
= \{ k \in [d]^p : \forall i \in [d], c_i = |\{ j \in [p] : k_j = i \}|
\}$ are the set of index vectors $k$ whose count profile is $c$.
For symmetric tensors $X$ and $Y$, $\innerp{X}{Y} = \innerp{\cvec(X)}{\cvec(Y)}$.
Later, we'll see that vectorization allow us to perform regression on tensors,
and collapsing simplifies our identifiability condition.

>>>>

% Goal of this paper
% This paper: first step in establishing provably correct estimation
% with simple mixture of linear regression
Our broad goal is to develop efficient provably consistent estimators for
discriminative latent-variable models.
In this paper, we provide a first step in this 
direction by proposing a new algorithm for a simple model,
\emph{a mixture of linear regressions} \cite{VieleTong2002}. % (MLG) ?

@@

% Norms
For a vector $X$,
let $\|X\|_\op$ denote the 2-norm.
For a matrix $X$,
let $\|X\|_*$ denote the nuclear (trace) norm (sum of singular values),
$\|X\|_F$ denote the Frobenius norm (square root of sum of squares of singular values),
$\|X\|_{\max}$ denote the max norm (elementwise maximum),
$\|X\|_\op$ denote the operator norm (largest singular value), and
$\sigma_k(X)$ be the $k$-th largest singular value of $X$.
For a $p$-th order tensor $X$,
let $\|X\|_* = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_*$ denote
the average nuclear norm over all $p$ unfoldings,
and let $\|X\|_\op = \frac{1}{p} \sum_{i=1}^p \|X_{(i)}\|_\op$
denote the average operator norm over all $p$ unfoldings.

Let $\vvec(X)$ be the vectorization of a $p$-th order tensor. For
example, if $X \in (\Re^{2})\tp{3}$, $\vvec(X) = (X_{111}, X_{112},
\cdots, X_{222})$.
For a tensor $X \in (\Re^d)\tp{p}$, let $\cvec(X) \in
\Re^{N(d,p)}, N(d,p) = \binom{d + p - 1}{p}$ be the collapsed vectorization of
$X$. For example, if $X \in \Re^{d \times d}$, $\cvec(X)
= (X_{ii} : i \in [d]; \frac{X_{ij} + X_{ji}}{\sqrt{2}} : i,j \in [d], i<j)$.
In general, each component of $\cvec(X)$ is indexed by a vector of
counts $(c_1, \dots, c_d)$ with total sum $\sum_i c_i = p$.  The value
of that component is $\frac{1}{\sqrt{|K(c)|}} \sum_{k \in K(c)} X_{k_1 \cdots k_p}$, where $K(c)
= \{ k \in [d]^p : \forall i \in [d], c_i = |\{ j \in [p] : k_j = i \}|
\}$ are the set of index vectors $k$ whose count profile is $c$.
We note that for a symmetric tensor $X$ and any tensor $Y$,
$\innerp{X}{Y} = \innerp{\cvec(X)}{\cvec(Y)}$; this property is not true
in general though.
Later, we'll see that vectorization allow us to perform regression on tensors,
and collapsing simplifies our identifiability condition.
